---
title: Numeric Example
output: pdf_document
---

```{r setup, include=FALSE,warning=FALSE,echo=FALSE,message=FALSE}
knitr::opts_knit$set(root.dir = "C:/Users/Christina/Desktop/mse-r/MSE-R")
```

## init
Set the library's directory first!

```{r,warning=FALSE,message=FALSE}
#Load Libraries and functions
setwd("C:/Users/Christina/Desktop/mse-r/MSE-R")
source("mse.R")
```

## Import precomputed data
Set the data's directory preferably in the variable 'filename'.
```{r }
filename<-"import/round1m1-1.xls.pre.dat"
```
Load the data in variables with meaningful names
```{r }
x<-import(filename)
g(header,noM,noU,noD,noAttr,distanceMatrices,matchMatrix,mate)%=%x
```

## Routines (calculate payoff matrix, inequalities members, dataArray)
```{r }
#Create payoffMatrix
Cx<-Cx(noAttr)
payoffMatrix<-CpayoffMatrix(noM,noU,noD,Cx,distanceMatrices,noAttr)

#Assign payoffMatrix numerical values (set x's)
xval<-c(1,2)
payoffMatrix<-assignpayoffMatrix(payoffMatrix,xval)
```

```{r }
#Create inequality members
ineqmembers<-Cineqmembers(mate)
```

```{r }
#Create Data Array
dataArray<-CdataArray(distanceMatrices,ineqmembers)
```

## Maximization

### Differential Evolution Method
The default DifferentialEvolution parameters:

\begin{table}[]
\centering
\begin{tabular}{lll}
option name & default value   & \\ \hline
lower,upper & -10,10          & two vectors specifying scalar real lower and upper bounds on each parameter to be optimized, so that the i-th element of lower and upper applies to the i-th parameter. The implementation searches between lower and upper for the global optimum (minimum) of fn.\\
CR          & 0.5             & crossover probability from interval [0,1]\\
trace       & FALSE           & Positive integer or logical value indicating whether printing of progress occurs at each iteration\\
itermax     & 100             & the maximum iteration (population generation) allowed\\
F           & 0.6             & differential weighting factor from interval [0,2]\\
NP          & 50              & number of population members. Defaults to NA; if the user does not change the value of NP from NA or specifies a value less than 4 it is reset when DEoptim is called as 10*length(lower). For many problems it is best to set NP to be at least 10 times the length of the parameter vector.\\
reltol      & 0.001           & relative convergence tolerance. The algorithm stops if it is unable to reduce the value by a factor of reltol * (abs(val) + reltol) after steptol steps\\
RandomSeed  & 0               &  Random Seed to be used for result reproducibility 
\end{tabular}
\end{table}

```{r }
#Objective function
coefficient1<-1
b<-c(2,1) #Define x1,x2,... values
obj<-objective(b)

#maximize function
lower <- c(-10, -10)
upper <- -lower
par<-list(lower=lower,upper=upper,NP=50,itermax=100,trace=FALSE,reltol=0.001,CR=0.5,F=0.6,RandomSeed=0)
x<-maximize(par)
g(bestmem,bestval)%=%x
print(bestmem)
print(bestval)
```

## Confidence Intervals